Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-09-25 paper/paper.tex

Furthermore, B2B closely relates to CCA \citep{cca_hotelling}, but departs from it in four main aspects. First, B2B is not symmetric between $X$ and $Y$: it aims to identify specific causal features. By contrast, CCA is symmetric between $X$ and $Y$, and aims to find $G$ and $H$ such that they project $X$ and $Y$ on maximally correlated dimensions. Second, CCA is based an eigenvector decomposition of $XH$ and $YG$ - the corresponding canonical components are thus mixing the $X$ features in way that limit interpretability. Third, CCA does not typically optimize two distinct regularization parameters. Finally, CCA does not use different data splits to estimate $G$ and $H$, and is thus prone to overfitting. Together, these differences may explain why B2B reliably outperform CCA on estimating causal influences (Fig. \ref{table:synthetic}). Extensions of CCA have been explored in neuroimaging (see \citep{de2019multiway} for brief review), but typically do not address the issue of causal detection.

>>>>

Furthermore, B2B closely relates to CCA \citep{cca_hotelling}, but departs from it in four main aspects. First, B2B is not symmetric between $X$ and $Y$: it aims to identify specific causal features by first optimizing over the decoders $G$ and then over $H$. By contrast, CCA is symmetric between $X$ and $Y$, and aims to find $G$ and $H$ such that they project $X$ and $Y$ on maximally correlated dimensions. Second, CCA is based a eigenvector decomposition of $XH$ and $YG$ - the corresponding canonical components are thus mixing the $X$ features in way that limit interpretability. Third, CCA does not typically optimize two distinct regularization parameters. Finally, CCA does not use different data splits to estimate $G$ and $H$. Together, these differences may explain why B2B reliably outperform CCA on estimating causal influences (Figs. \ref{fig:percondition} and \ref{fig:auc_plots}). Extensions of CCA have been explored in neuroimaging (see \citep{de2019multiway} for brief review), but typically do not address the issue of causal detection.
